\paperTitle

### 2014-01-31 doc/icml2014/directed.tex
Merged percy's chagnes and made some minor fixes

\LearnMarginals~ combines two consistent algorithms, \TensorFactorize and
\LearnClique, \todo{too much space after LearnClique} and is thus consistent itself.
\todo{did they prove this; if so just say "they show", not "we can show"}
Using results from
  \citet{anandkumar12moments,anandkumar13tensor} we can show that
  learning $\mOpp{v_1}{i}$ for the bottleneck $h_i$ with views $x_{v_1},
  x_{v_2}, x_{v_3}$ has the following sample complexity,
  \todo{define hat O}
  \todo{max subscript is misaligned}
\begin{align*}
  \|\mOpphat{v_1}{i} - \mOpp{v_1}{i}\|^2_F &= \frac{1}{\sqrt{n}} O\left( \frac{k {\pi\oft{i}}_{\max}^2}{\sigma_k(M_{v_1,v_2})^5} \right). 
\end{align*}

>>>>

\LearnMarginals combines two consistent algorithms, \TensorFactorize and
\LearnCliqueNs, and is thus consistent itself.
%\todo{did they prove this; if so just say "they show", not "we can show"}
%Using results from
%  \citet{anandkumar12moments,anandkumar13tensor} we can show that
%  learning $\mOpp{v_1}{i}$ for the bottleneck $h_i$ with views $x_{v_1},
%  x_{v_2}, x_{v_3}$ has the following sample complexity,
%  \todo{define hat O}
%  \todo{max subscript is misaligned}
%\begin{align*}
%  \|\mOpphat{v_1}{i} - \mOpp{v_1}{i}\|^2_F &= \frac{1}{\sqrt{n}} O\left( \frac{k {\pi\oft{i}}_{\max}^2}{\sigma_k(M_{v_1,v_2})^5} \right). 
%\end{align*}
